Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-07-09 paper/re-pro-badge.tex
automatically reproduce paper

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/68c3ef6}{68c3ef6} on 2024-07-08 at 18:58:43 UTC.

>>>>

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/3f5eb52}{3f5eb52} on 2024-07-09 at 06:06:30 UTC.
